\documentclass[a4paper,english, 11pt]{article}

\usepackage[a4paper,inner=2.5cm,outer=2.5cm,top=2.5cm,bottom=2.5cm,pdftex]{geometry} 
\usepackage{hyperref}
\hypersetup{colorlinks=true,linkcolor=blue, linktocpage}

\newcommand{\emailme}{\href{mailto:lukem@unis.no}{lukem@unis.no}}

\title{UNIS data management plan}
\date{\today\\v0.1}
\author{Luke Marsden (\emailme)}

\begin{document}
\maketitle
\tableofcontents

\newpage

\section{Admin details}
\label{s:admin}

Data management plan of the University Centre in Svalbard (UNIS). Funding comes from .... and other scientific projects involving UNIS staff.

\section{Data summary}
\label{s:data}

\section{FAIR data}
\label{s:fair}

UNIS is committed to publishing data that are Findable, Accessible, Interoperable and Reusable (FAIR). UNIS follows the recommendations of the \href{https://sios-svalbard.org/sites/sios-svalbard.org/files/common/SIOS_Data_Management_Plan.pdf}{SIOS Data Management Plan} (section 3) on how to make data FAIR. 

\section{Allocation of resources}
\label{s:resources}

Currently, there is no overview of the total costs for making UNIS data FAIR. 

All data relevant to Svalbard should be made available via the SIOS data access portal (\url{https://sios-svalbard.org/metsis/search}). Priority should therefore be given to publish to data centres that contribute to the SIOS data access portal. These are listed in the section 'Allocation of resources' of the \href{https://sios-svalbard.org/sites/sios-svalbard.org/files/common/SIOS_Data_Management_Plan.pdf}{SIOS Data Management Plan}.

Of these data centres, Norwegian data centres should be prioritised. NIRD (the National Infrastructure for Research Data) host a data centre funded by the research council of Norway (RCN). This is not attached to any individual research institution and therefore may be particularly suitable for many UNIS datasets. However, other data centres that contribute to SIOS can be used if collaborating with employees of other research institutions or if the data centre if preferable.

Data published to a data centre that does not contribute to the SIOS data access portal should be linked manually using a metadata collection form hosted by SIOS (\url{https://sios-svalbard.org/metadata-collection-form}).  

\section{Data security}
\label{s:security}

As mentioned in section \ref{s:resources}, UNIS data should be published in data centres that contribute to the SIOS data access portal. Therefore, as mentioned in the 'Data security' section of the \href{https://sios-svalbard.org/sites/sios-svalbard.org/files/common/SIOS_Data_Management_Plan.pdf}{SIOS Data Management Plan}, the security of published UNIS datasets relies on the security implemented by these data centres.

\section{Ethical aspects}
\label{s:ethics}

Ethical aspects are handled according to the UNIS Data Policy. Generally, UNIS is not handling sensitive research data, but UNIS follows the principle of "as open as possible, as closed as necessary".

\section{Other}
\label{s:other}

The UNIS data management plan is, as mentioned above, based on the existing \href{https://sios-svalbard.org/sites/sios-svalbard.org/files/common/SIOS_Data_Management_Plan.pdf}{SIOS Data Management Plan}. It has been modified to suit the needs of UNIS. Wherever possible, this document refers to the SIOS data management plan instead of duplicating text. Therefore, the recommendations provided in the UNIS data management plan will evolve as the SIOS data management plan evolves. 

\end{document} 